### 2017-09-08 Sections/a_new_frontier_towards_the_singularity.tex
master text from Tim Byrnes - not edited in

\input{Sections/the_era_of_quantum_supremacy}

@@

\input{Sections/the_economics_of_the_quantum_internet}

@@

\input{Sections/the_global_virtual_quantum_computer}

@@

\input{Sections/security_implications_of_the_global_quantum_internet}

@@

\input{Sections/geostrategic_quantum_politics}

@@

\input{Sections/the_quantum_space_race}

@@

\input{Sections/the_quantum_mind}

@@

\input{Sections/the_quantum_singularity}

>>>>

\input{Sections/essay_the_era_of_quantum_supremacy}

@@

\input{Sections/essay_the_economics_of_the_quantum_internet}

@@

\input{Sections/essay_the_global_virtual_quantum_computer}

@@

\input{Sections/essay_security_implications_of_the_global_quantum_internet}

@@

\input{Sections/essay_geostrategic_quantum_politics}

@@

\input{Sections/essay_the_quantum_space_race}

@@

\input{Sections/essay_the_quantum_mind}

@@

\input{Sections/essay_the_quantum_singularity}

### 2017-09-08 Sections/authors.tex
Minor updates. Author update
master text from Tim Byrnes - not edited in

@@

@@

\author{He-Liang Huang}
\affiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\affiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\affiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}

@@

@@

%\author{Samuel I. Marks}
%\affiliation{Sydney Medical School, University of Sydney, Australia}

@@

@@

@@

@@

>>>>

%
% Peter P. Rohde
%

@@

%
% Zu-En Su
%

@@

%
% He-Liang Huang
%

\author{He-Liang Huang}
\affiliation{Hefei National Laboratory for Physical Sciences at Microscale and Department of Modern Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\affiliation{CAS Centre for Excellence and Synergetic Innovation Centre in Quantum Information and Quantum Physics, University of Science and Technology of China, Hefei, Anhui 230026, China}
\affiliation{CAS-Alibaba Quantum Computing Laboratory, Shanghai 201315, China}
\affiliation{Henan Key Laboratory of Quantum Information \& Cryptography, Zhengzhou Information Science and Technology Institute, Zhengzhou, Henan 450000, China}

%
% Si-Hui Tan
%

@@

%
% Nana Liu
%

@@

%
% Ryan L. Mann
%

@@

%
% Jonathan P. Dowling
%

@@

%
% Tim Byrnes
%

\author{Tim Byrnes}
\affiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\affiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\affiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\affiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\affiliation{Department of Physics, New York University, New York, NY 10003, USA}

%
% William J. Munro
%

@@

%
% Chao-Yang Lu
%

@@

%
% Christopher Altman
%

### 2017-09-08 Sections/optical_encoding_of_quantum_information.tex
master text from Tim Byrnes - not edited in

Unfortunately, cat states are notoriously difficult to prepare, and extremely sensitive to loss (Sec.~\ref{sec:single_phot_enc}) and dephasing (Sec.~\ref{sec:dephasing_error}). This arises because loss of a single photon flips the parity of the state to an orthogonal one, meaning that as $\alpha$ increases, the state is exponentially more susceptible to becoming a mixture of the logical basis states.

>>>>

Unfortunately, cat states are notoriously difficult to prepare, and extremely sensitive to loss (Sec.~\ref{sec:single_phot_enc}) and dephasing (Sec.~\ref{sec:dephasing_error}). This arises because loss of a single photon flips the parity of the state to an orthogonal one, meaning that as $\alpha$ increases, the state is exponentially more susceptible to decohering into a mixture of the logical basis states.
